\documentclass[logo,bsc,singlespacing,parskip,online]{infthesis}
\usepackage{ugcheck}

\usepackage{microtype} % recommended, but you can remove 
\usepackage[numbers]{natbib} 
\usepackage{hyperref} 
\begin{document}
\begin{preliminary}

\title{Lead Sheet Transcription}

\author{Pierre Lardet}

\course{Computer Science and Mathematics}


\project{4th Year Project Report}


\date{\today}

\abstract{
This skeleton demonstrates how to use the \texttt{infthesis} style for
undergraduate dissertations in the School of Informatics. It also emphasises the
page limit, and that you must not deviate from the required style.
The file \texttt{skeleton.tex} generates this document and should be used as a
starting point for your thesis. Replace this abstract text with a concise
summary of your report.
}

\maketitle

\newenvironment{ethics}
   {\begin{frontenv}{Research Ethics Approval}{\LARGE}}
   {\end{frontenv}\newpage}

\begin{ethics}
This project was planned in accordance with the Informatics Research
Ethics policy. It did not involve any aspects that required approval
from the Informatics Research Ethics committee.

\standarddeclaration
\end{ethics}


\begin{acknowledgements}
Thank you to my two lovely supervisors, \hyperlink{https://homepages.inf.ed.ac.uk/amos/index.html}{Prof. Amos Storkey} and \hyperlink{https://www.acoustics.ed.ac.uk/people/dr-alec-wright/}{Dr. Alec Wright}, for allowing me to fulfil my desire for such a personally fulfilling project. They for provided me with invaluable guidance on both this project and research in general, which I will take forward to future research. I would also like to thank my friends and family for their unwavering support throughout the year, and for their patience and understanding when I was too busy to spend time with them.
\end{acknowledgements}


\tableofcontents
\end{preliminary}


\chapter{Introduction}

\section{Motivation}

\section{Aims}

\section{Outline}


\section{Citations}
\cite{donahue2022melodytranscriptiongenerativepretraining}


\chapter{Background \& Related Work}

\section{Lead Sheets}

Lead sheets are a form of musical notation that contain both the melody and 

\section{Music Transcription}

\section{Deep Learning}

\section{Related Work}

\chapter{Experiments}

\section{Data}

\section{Models}

\section{Training}

\section{Evaluation}

\chapter{Results}

\section{Quantitative Results}

\section{Qualitative Results}


\chapter{Conclusions}


\bibliographystyle{plain}
% \bibliographystyle{plainnat}
\bibliography{references}


% You may delete everything from \appendix up to \end{document} if you don't need it.
\appendix

\chapter{First appendix}

\section{First section}


\end{document}
