\begin{preliminary}

    \title{Lead Sheet Transcription}
    
    \author{Pierre Lardet}
    
    \course{Computer Science and Mathematics}
    
    
    \project{4th Year Project Report}
    
    
    \date{\today}
    
    \abstract{
    This skeleton demonstrates how to use the \texttt{infthesis} style for
    undergraduate dissertations in the School of Informatics. It also emphasises the
    page limit, and that you must not deviate from the required style.
    The file \texttt{skeleton.tex} generates this document and should be used as a
    starting point for your thesis. Replace this abstract text with a concise
    summary of your report.
    }
    
    \maketitle
    
    \newenvironment{ethics}
       {\begin{frontenv}{Research Ethics Approval}{\LARGE}}
       {\end{frontenv}\newpage}
    
    \begin{ethics}
    This project was planned in accordance with the Informatics Research
    Ethics policy. It did not involve any aspects that required approval
    from the Informatics Research Ethics committee.
    
    \standarddeclaration
    \end{ethics}
    
    
    \begin{acknowledgements}
    Thank you to my two lovely supervisors, \hyperlink{https://homepages.inf.ed.ac.uk/amos/index.html}{Prof.~Amos Storkey} and \hyperlink{https://www.acoustics.ed.ac.uk/people/dr-alec-wright/}{Dr.~Alec Wright}, for allowing me to fulfil my desire for such a personally fulfilling project. They for provided me with invaluable guidance on both this project and research in general, which I will take forward to future research. I would also like to thank my friends and family for their unwavering support throughout the year, and for their patience and understanding when I was too busy to spend time with them.
    \end{acknowledgements}
    
    
    \tableofcontents
    \end{preliminary}